### 2019-05-28 doc/chapters/trying_verify_checktx.tex
text

\chapter{Trying to Verify checkTransaction}
\label{chap:connecting}

\section{Integration (Versionskonflikte, neues Plugin)}
During this work, Stainless bumped the sbt plugin from version 0.13.17 to 1.2.8 and Scala from 2.11.12 to 2.12.8.
So this section might be out of date now.

>>>>

\chapter{Trying to Verify checkTransaction}
\label{chap:connecting}
This chapter describes the process we've made on trying to integrate Stainless in Bitcoin-S.
It shows the differences between the error reporting by the sbt plugin and the JAR.
Finally, during our work on Bitcoin-S we found a bug that we explain along its corresponding bug fix.

\section{Integration}
During this work, Stainless bumped the sbt plugin from version 0.13.17 to 1.2.8 and Scala from 2.11.12 to 2.12.8.
So this section might be out of date now.
